Generative Adversarial Networks

### 2017-12-02 cs6735/project/draft.tex
added progressive

\section{Applications}
GANs are an exciting idea that are currently leading the frontier of deep generative models.
\subsection{Divergence Measures}
\subsection{Image Quality}
Hinton's Capsule Network
Progressive GANs
\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
\subsection{Feature Learning}
\subsection{Semi-Supervised Learning}
\subsection{Reinforcement Learning}
\subsection{Image to Image Translation} \label{sec:img2img}

\section{Research Frontiers}
Evaluation, instability, mode collapse

Reinforcement learning

@@

>>>>

\subsection{Progressive GANs}
Progressive GANs offer extend the DCGAN architecture by altering their training process. Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within both the generator and discriminator. Each new convolution is \texit{blended in} and is added after the current GAN converges which permits the generator to progressively discover the image distribution. Combined with new normalization techniques, progressive GANs allow for much higher resolution images to be generated \citep{2017arXiv171010196K}. The experimental results offer promising new directions for GAN research and applications.

\begin{figure}
\centering
\includegraphics[scale=0.45]{progrssive_growing}
\caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \texit{et al.} \citep{2017arXiv171010196K}. The generator and discriminator begin at $4x4$ resolution and progressively grow generate and discriminate $1024x1024$ resolution images.}
\label{fig:CumulativeNumberofGANPapersbyMonth}
\end{figure}

\section{Latent Space}
\section{Applications}
GANs are an exciting idea that are currently leading the frontier of deep generative models.

\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
\subsection{Image Generation}
\subsection{Image to Image Translation} \label{sec:img2img}
\subsection{Super Resolution}

\section{Research Frontiers}
Evaluation, instability, mode collapse
\subsection{Divergence Measures}
\subsection{Image Quality}
\subsection{Reinforcement Learning}
Reinforcement learning

@@

GANs build their own representations of the data they
are trained on, and in doing so produce structured geometric
vector spaces for different domains
